---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
library(fractalplotr)
```


# fractalplotr

This package lets you create and plot fractals.

currently implemented:

* [Dragon curve](https://en.wikipedia.org/wiki/Dragon_curve)
* [Mandelbrot set](https://en.wikipedia.org/wiki/Mandelbrot_set)
* [Sandpile](https://en.wikipedia.org/wiki/Abelian_sandpile_model)

planned:

* [Julia set](https://en.wikipedia.org/wiki/Julia_set)
* [Ulam-Warburton cellular automaton](https://en.wikipedia.org/wiki/Ulam%E2%80%93Warburton_automaton)
* [toothpick pattern](https://en.wikipedia.org/wiki/Toothpick_sequence)


## Installation

`fractalplotr` is not on CRAN. You can install the most recent version from GitHub using the devtools package:
``` {r install, eval = FALSE}
# install.packages("devtools")
devtools::install_github("bastihz/fractalplotr")
```
RStudio's integrated package updater won't detect updates in packages installed from GitHub. I recommend running
``` {r update, eval = FALSE}
devtools::update_packages()
```
in regular intervals to check for updates from those sources.


## Examples

### Dragon curve

```{r dragon}
d <- dragon_curve(12)
plot(d, col = "forestgreen")
```


### Mandelbrot set

```{r mandelbrot}
blue_to_black <- colorRampPalette(c(rgb(0, 0, 0.5), "white", rgb(1, 0.75, 0), 
                                    "darkred", "black"))
m <- mandelbrot(
    1200, 
    1200,
    re_width = 2.5,
    center = -0.75,
    color_palette = blue_to_black(128),
    color_mode = "smooth"
)
plot(m)
```


### Sandpile

```{r sandpile}
s <- sandpile(1e5, c("white", "yellow", "orange", "red"))
plot(s)
```
