---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(fractalplotr)
```
# fractalplotr

The goal of fractalplotr is to ... (FIXME)
This package is currently under heavy construction. Nothing works and everything
is on fire.

## Installation

You can install fractalplotr from GitHub with:

``` {r install, eval = FALSE}
install.packages("devtools")
devtools::install_github("bastihz/fractalplotr")
```
## Examples

TODO: better image resolution, maybe a little smaller images? See how it looks on the phone and the laptop.
# FIXME: If I can't set the size via the chunk then I could just generate and save the pictures using an r chunk and include them using normal markdown (center aligned, look for examples). In this case tweak the knitr::opts chunk. See for example the usesthis readme and how it includes the hexagonal logo.

**Dragon curves** (TODO: link to wikipedia)

```{r dragon}
d <- dragon_curve(12)
plot(d)
```

**Mandelbrot sets** (TODO: link to wikipedia)

```{r mandelbrot}
m <- mandelbrot(
    800, 
    600, 
    color_palette = colorRampPalette(c("black", "green"))(128)
)
plot(m)
```


**Sandpiles** (TODO: link to wikipedia)


```{r sandpile}
s <- sandpile(1e5)
plot(s)
```

